Double Trouble: Understanding Sex Differences in Synthetic Lethal interactions in Human Cancers \\~\\ Project Updates

### 2023-07-15 july18meeting_pres2/may30ccgmeeting.tex
Updates

	\section{Synthetic Lethality}
	\begin{frame}{Using DE Genes to Find Sex-Specific Synthetic Lethal Pairs}
		content...
	\end{frame}

@@

	\begin{frame}
		content...
	\end{frame}

>>>>

	\section{Synthetic Lethality}
	\begin{frame}{Next Steps: Using DE Genes to Find Sex-Specific Synthetic Lethal Pairs}
		\begin{enumerate}
			\item Find all potential gene pair combinations using down regulated genes specific to males and specific to females \newline

			\textcolor{blue}{${280 \choose 2 } = 39060$ Downregulated Male Pairs \newline}
			\textcolor{yellow}{${70 \choose 2 } = 2415$ Downregulated Female Pairs}

			\item Check whether the co-inactivation of a candidate SL pair is underrepresented in tumor samples
		\end{enumerate}
	\end{frame}

@@
